Near infrared metrology of high performance silicon immersion gratings

### 2015-03-25 chSPIE_2010_JWST/mgs_spie_2010_v1_5.tex
remove duplicate references in the bib file and rename some citation keys to ADS style

\subsection{Groove Geometry}
We form the grooves in the monolithic substrates from which we fabricate the grisms by taking advantage of the significantly different rates at which certain chemicals etch through the different planes in crystalline structure\cite{Marsh07,Tsang1975}.  In our process a solution of KOH etches approximately 60 times faster across the 100 plane than across the 111 plane and a suitably oriented mask of stripes will form triangular grooves at the intersection of 111 planes.  The intersecting planes form an angle of $71\,^{\circ}{\rm}$.  For blaze angles greater than $8\,^{\circ}{\rm}$, this acute angle will result in shadowing of one groove by another in transmission with the amount of shadowing a function of the blaze angle (see Figure 6 of Mar et al. (2006)\cite{Mar06}).  For small prism opening angles, it is not the acute groove vertex but rather the small dams along the grating surface that lead to groove filling factors less than one.  We need the dams to serve as etch stops between the grooves.  For the JWST gratings, the grating constant was 15.36 $\mu$m and the final dam width was about 1.5 $\mu$m.  At the $6.16 \,^{\circ}{\rm}$ opening angle of the JWST prisms, the dams are responsible for the filling factor loss.  The geometric blockage whether by the dams or by the lip of the neighboring acute groove leads to loss in two ways:  direct blockage of the light and, via Babinet's principle, diffraction of an equal amount of light into unwanted orders.  For the geometric blockage of $\sim10\%$ in the JWST grisms, the maximum theoretical transmission is then 0.81.

\subsection{Microscopic Surface Roughness}
While the etching process results in remarkably flat grooves, point defects in the structure of the crystalline silicon grating substrates can lead to local pits and hillocks, that is, to roughness on various scales, as the anisotropic etching produces the blazed grooves.  The consequences of this roughness are difficult to measure directly as the scattered light produced as a result of it is generally on large angular scales with low peak amplitudes.  Instead, the best ways to evaluate this possible loss mechanism is to examine the roughness of the surfaces directly.  We have done this for an earlier set of grating surfaces using atomic force microscopy\cite{Marsh07} and concluded that the integrated diffuse scattered light due to small-scale roughness is 0.005\% for a Si grism in operation at 3.7$\mu$m.  We have also used interferometric metrology of roughness within individual grooves in the more demanding context of immersion grating production (see Wang et al. in this volume\cite{Wang10}) and find that the loss should be about 0.006\%  if such surfaces are used in transmission.

>>>>

\subsection{Groove Geometry}
We form the grooves in the monolithic substrates from which we fabricate the grisms by taking advantage of the significantly different rates at which certain chemicals etch through the different planes in crystalline structure\cite{2007ApOpt..46.3400M,Tsang1975}.  In our process a solution of KOH etches approximately 60 times faster across the 100 plane than across the 111 plane and a suitably oriented mask of stripes will form triangular grooves at the intersection of 111 planes.  The intersecting planes form an angle of $71\,^{\circ}{\rm}$.  For blaze angles greater than $8\,^{\circ}{\rm}$, this acute angle will result in shadowing of one groove by another in transmission with the amount of shadowing a function of the blaze angle (see Figure 6 of Mar et al. (2006)\cite{Mar06}).  For small prism opening angles, it is not the acute groove vertex but rather the small dams along the grating surface that lead to groove filling factors less than one.  We need the dams to serve as etch stops between the grooves.  For the JWST gratings, the grating constant was 15.36 $\mu$m and the final dam width was about 1.5 $\mu$m.  At the $6.16 \,^{\circ}{\rm}$ opening angle of the JWST prisms, the dams are responsible for the filling factor loss.  The geometric blockage whether by the dams or by the lip of the neighboring acute groove leads to loss in two ways:  direct blockage of the light and, via Babinet's principle, diffraction of an equal amount of light into unwanted orders.  For the geometric blockage of $\sim10\%$ in the JWST grisms, the maximum theoretical transmission is then 0.81.

\subsection{Microscopic Surface Roughness}
While the etching process results in remarkably flat grooves, point defects in the structure of the crystalline silicon grating substrates can lead to local pits and hillocks, that is, to roughness on various scales, as the anisotropic etching produces the blazed grooves.  The consequences of this roughness are difficult to measure directly as the scattered light produced as a result of it is generally on large angular scales with low peak amplitudes.  Instead, the best ways to evaluate this possible loss mechanism is to examine the roughness of the surfaces directly.  We have done this for an earlier set of grating surfaces using atomic force microscopy\cite{2007ApOpt..46.3400M} and concluded that the integrated diffuse scattered light due to small-scale roughness is 0.005\% for a Si grism in operation at 3.7$\mu$m.  We have also used interferometric metrology of roughness within individual grooves in the more demanding context of immersion grating production (see Wang et al. in this volume\cite{Wang10}) and find that the loss should be about 0.006\%  if such surfaces are used in transmission.

### 2015-03-25 chSPIE_2012_CA1/chapter-2012-CA1.tex
rename the SPIE 2012 paper to a chapter, document compiles great
remove duplicate references in the bib file and rename some citation keys to ADS style

Immersion gratings are diffraction gratings illuminated within a high refractive index optical material, which provides increased spectral resolving power compared to diffraction gratings of comparable size illuminated in air or vacuum.  Scientific demands for high spectral resolving power combined with engineering demands for compact spectrographs make immersion gratings an attractive technology.  This report chronicles the lab performance of CA1a, an immersion grating made of silicon ($n_{Si}\sim3.4$).  CA1a or its spare CA1b will serve as the primary dispersive optical element for the Immersion Grating Infrared Spectrometer, IGRINS\cite{yuk2010}.  We have reported on immersion grating design and fabrication elsewhere\cite{marsh2007}.  Wang et al. 2010\cite{wang2010} reported on the science requirements for, fabrication of, and optical testing results of CA1, the parent Si boule puck from which CA1a was cut.  Since 2010 we have cut and polished two optical devices from CA1, and report here on their performance \emph{in immersion}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview} 
Figure \ref{fig:CA1aphoto} shows a photo of the final immersion grating CA1a after cutting, polishing, AR coating, and aluminization.  The trapezoidal side profile is a relic from the shape of the parent substrate and our cutting strategy.  The optically active volume is the prism shown above the dashed line in the photo in Figure \ref{fig:CA1aphoto}.  We left on additional silicon to strengthen the thin end of the prism wedge.  The front entrance face has a multi-layer dielectric anti-reflection (AR) coating, which, based on direct measurements off the CA1a entrance face, has a reflectivity  $<1\%$ across the 1.4$-$2.5 $\mu$m range.  The grating grooves were aluminized with a conformal Al layer.  Cryogenic testing of heritage gratings demonstrated that the conformal layer of Al is robust to typical cryogenic thermal cycling\cite{marsh2007}. We have not yet cooled CA1a.

\begin{figure}
  \centering
  \subfloat[CA1a photo]{\label{fig:CA1aphoto}\includegraphics[height=5cm]{chSPIE_2012_CA1/figs/ca1_bartest2}}
	~
%  \subfloat[CA1a drawing]{\label{fig:CA1adraw}\includegraphics[page=1, trim=24cm 15.15cm 2cm 5cm, clip=true, totalheight=0.2\textheight ]{APRA_BOULE_29MM_R3_CA1_X14_2011-03-08}}
   \subfloat[CA1a drawing]{\label{fig:CA1adraw}\includegraphics[height=4cm]{chSPIE_2012_CA1/figs/ca1a_drawing}}
  \caption{Photo and design drawing of the immersion grating CA1a in the lab in August 2011.  The entrance face is on the right, with a light green color in the photo (color available in the digital manuscript), which is due to the AR coating.  The grating surface is on the top with microscopic grating lines perpendicular to the long edge of the grating.  In operation a 25 mm circular beam will be incident on the entrance face and will project into an ellipse on the grating surface as seen in the drawing.  The dispersed light will reemerge from the entrance face.  The units in the drawing are mm.  The parent substrate and grating geometry are pictured in Figures 1, 3, and 4 in Wang et al. 2010\cite{wang2010}.  Those figures reveal how the CA1a trapezoid shape and curved rear edge derive from the parent substrate shape.}
  \label{fig:gram}
\end{figure}

@@

We produce the grating grooves by photolithography and anisotropic chemical wet etching\cite{marsh2007,wang2010}.  This process has some special features.  The wet etching process makes acute angle grooves, not 90$^\circ$ grooves, as illustrated in Figure \ref{fig:CA1aSEM}.  The groove apex angle $A=70.5^\circ$ is the intersection of two 111 Si crystal planes.  We anticipated an apex angle widened by 0.8$^\circ$ on both sides, for a net apex angle of about $A=72.1^\circ$.  A finite but small amount of etching accross the 111 crystal planes causes the small 0.8$^\circ$ angular correction\cite[Figure 5]{marsh2007}.  The anisotropic correction similarly decreases the blaze angle $\delta$ by $\Delta \delta = 0.8^\circ$.  This effect must be accounted for, first at the time of the initial x-ray orientation and cutting of the parent substrate and second at the time of cutting the immersion prism from the Si parent substrate.  We verified the delivered blaze angle after wet etching but before cutting our immersion grating prism by measuring the relative intensity of eight diffracted orders in reflection in air at the air-Si grating interface.  We made a simple scalar diffraction theory model and compared it to the observed intensity of the eight orders surrounding order 82, the brightest observed order at 632.8 nm in front-surface reflection.  The measurements were performed in the Littrow configuration.  The model predicted the effect of the blaze envelope as a function of incidence angle.  We found $\delta=71.63\pm0.20^\circ$, consistent within the uncertainty with $\delta = R3$, so we cut the front face to R3.  The apex and blaze angles are conspicuous in the SEM cross section (Figure \ref{fig:CA1aSEM}).  Importantly, the groove apex shows a sharp peaked tip with no evidence of a flat bottom, which can occur in incomplete wet etching.  Flat bottoms cause a direct efficiency loss by diffracting light away from the blaze.  In the right panel of Figure \ref{fig:CA1aSEM} the optically active facets are highlighted.  The flat groove tops on the grating surface are artifacts of the groove formation process.  Specifically, nitride coated groove tops serve as anisotropic wet etch dams.  It is clear from the annotated SEM micrograph that the groove tops are shadowed for light incident at or close to the blaze angle.  The groove tops will be shadowed so long as the ratio of the grating top $t$ to pitch $\sigma$ ratio satisfies the condition:
\[ 
\frac{t}{\sigma} < \frac{1}{1+\frac{ \tan (A) }{ \tan (\delta{}) }}, 
 \] 
For our grating, $t/\sigma=0.36<0.49$, so the optically active groove facets fully shadow the groove tops as planned.  The SEM micrographs are not sensitive enough to small ($\sim5$ nm) scale groove position errors, so detailed optical and IR metrology is necessary to evaluate the performance.

%-------------
   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=7cm]{chSPIE_2012_CA1/figs/CA1_SEM_cross3}
   \end{tabular}
   \end{center}
   \caption[CA1a SEM]{ \label{fig:CA1aSEM}  Scanning electron micrograph (SEM) of a $\sim$100 $\mu$m cross section of a scrap portion of the immersion grating CA1.  The left panel is the unaltered SEM.  The right panel is a schematic illustrating the grating specifications and the geometry of incident and diffracted beams (thick black line with arrows).  The beam is incident from the left, and diffracts at the facets at the silicon/aluminum interface.  The incident angle $\alpha$ and diffracted beam $\beta$ are measured from the grating normal (shown in blue).  The blaze angle $\delta$ is set by the orientation of the crystal planes with respect to the grating surface.  This angle was designed to be $\delta=71.56^\circ$, which is the angle whose tangent is 3.  The optically active facets are highlighted as short red vertical lines (\emph{color online}).  The regions of the grating above the dashed line do not see the beam.  In the IGRINS design and in our lab testing there is a small out of plane angle $\gamma$ not shown here.  The apparent hillock artifacts on the grating facets are a result of the cross-section preparation process, the measured\cite{wang2010} surface flatness is 1.7 nm.}
   \end{figure} 
%-------------

\section{Efficiency} 
For optimal performance immersion gratings should be as efficient as possible.  The IGRINS specification for immersion grating efficiency is 65-70\% peak on blaze\cite{wang2010}. We directly measured the AR-coated entrance face reflective loss at $<1\%$ over the measured range $1500-2300$ nm.  From measurements of the microscopic surface roughness\cite{wang2010} we expect scattered light from microscopic surface roughness to be $<0.5\%$.  We directly measured the immersion grating efficiency as a function of wavelength with a custom scanning monochromator setup in our lab, described in the Section \ref{sec:GTA}.  The reference mirror was aluminum on glass, so the absolute grating efficiency is about 3.5\% lower than reported here, assuming aluminum reflectance of 95\% in the near-IR.  Recall that the grating grooves are aluminized, so the reported relative efficiency is a good indicator of how well the bulk of the immersion grating is performing.  The measurement shown in figure \ref{fig:CA1a-efficiency} has 1 nm bandwidth, with 1nm sampling over the range $1500-2300$ nm.  The measured peak on-blaze efficiency is between 70\% and 80\% across all 43 orders, except for order 120 which has a peak efficiency of 68\%.  CA1a was measured with an out of plane angle \cite{schroeder1987}, $\gamma \sim 2.6^\circ$ in immersion.  We only coarsely controlled the incidence angle $\alpha$ in our efficiency measurement, with $\alpha \sim \delta$ to within about 2$^\circ$.  Accordingly, we measured some angularly dependent diffraction loss that one would expect if orders diffracted into the grating sidewalls.  It is best to have $\alpha > \delta$ so that the blaze envelope is centered at $\beta < \delta$.

@@

\section{Refractive index dependence}
The refractive index of silicon is wavelength and temperature dependent, so the blaze pattern in Figure \ref{fig:CA1a-efficiency} will be different at the cryogenic operating temperature of an IR spectrograph.  Precise measurements for crystalline Si are available for the CHARMS group at Goddard\cite{frey2006}.  The right panel of figure \ref{fig:CA1a-diffrac} shows the refractive index as a function of wavelength for 296 K, 273 K, and 77K, using the Sellmeier equation from the Goddard group and assuming vacuum wavelengths.  The index goes from about 3.483 to 3.445 in the wavelength range 1.5 to 2.3 $\mu$m, which is a change of about 1\%.  The index decreases by an average of 0.8\% from room temperature to 77K.  The index intimately controls both the diffraction angle $\beta$ at the Si-Al grating interface via the grating equation, and the refraction angle $\theta$ at the Si-vacuum interface via Snell's law.  For example the wavelength $\lambda=2.290 \;\mu$m at room temperature is diffracted to 78th order near the peak of the blaze.  Reducing the temperature to 77K decreases the index of refraction by 0.8\%. This puts $\lambda= 2.290 \;\mu $m into 77th order, which is at the edge of the blaze.  The grating period $\sigma$ also shrinks by a factor of the coefficient of thermal expansion (CTE) of Si, $\alpha \sim 3\times10^{-6}/^\circ$C.  From room temperature to 77K the fractional shrinkage is about 0.06\%, which is an order of magnitude less than the effect of the index of refraction.  Furthermore, the CTE effect will have no effect at the Si-vacuum interface.

\begin{figure}
\begin{center}
 \begin{tabular}{c}
    \includegraphics[width=1.0\textwidth]{chSPIE_2012_CA1/figs/CA1a_diffrac}
   \end{tabular}
  \end{center}
  \caption[CA1a Diffraction]{\label{fig:CA1a-diffrac} Measured and predicted diffraction angles for CA1a.  The right panel is the index of refraction as a function of wavelength\cite{frey2006} for T = 296, 273, and 77 K.  The left panel is the angular position of diffracted beams as a function of wavelength.  The almost vertical lines are approximately 1 free spectral range of the observed 43 diffraction orders for $1500 < \lambda (\textrm{nm}) < 2300$ in air at T = 296K.  The order numbers for every fifth order, starting at 78th order are marked at the top.  The black diamonds are the observed peaks of the blaze efficiency (cf. figure \ref{fig:CA1a-efficiency}).  The measurements longward and shortward of $\lambda=1870$ nm have slightly different incidence $\alpha$ angles, which jogged the the blaze center positions.  The red $\ast$, green square, and blue $\times$ demarcate the expected positions of beams from scalar optics diffraction and refraction theory assuming a Si refractive index at the temperatures of T=296, 273, and 77 K, respectively.  The model corrects for $\alpha \neq \delta$ measurements for $\lambda < 1870 $ nm, causing a jog in the $\theta(\lambda)$ trend highlighted by the vertical black dashed lines.  The temperature change shifts the position of diffracted beams by an entire order.}
\end{figure}

@@

The major problem with periodic errors is that they cause symmetric ghosts surrounding the main diffraction peak.  The intensity of the ghosts relative to the main peak is related to the periodic error amplitude by\cite{marsh2007,james2007,wang2010}:
\begin{eqnarray}
	\frac{I_{\textrm{ghost}}}{I_{\textrm{line}}}= \left \lbrack \frac{2\pi n}{\lambda} \xi \sin{\delta} \right \rbrack ^2
\end{eqnarray}
where $\xi$ is the amplitude of the spacing error.  Figure \ref{fig:PSFzygo} shows a logarithmically scaled PSF from optical interferometry of CA1a in reflection from the aluminized surface in air at 632.8 nm over a 25 mm circular aperture.  The measured intensity of the ghost relative to the main peak is $I_{g}/I_{0}=9\times10^{-4}$.  Optical spectral purity lab measurements at 632.8 nm are higher by 20\%.  Measurements at 543 nm (comparable to 1.87 $\mu$m in immersion), show a level of $I_{g}/I_{0}=1.6\times10^{-3}$, which is 30\% greater than one would expect from scaling interferometrically derived intensity at 632.8 nm.  Extrapolating the interferometrically derived intensity to 1.45 $\mu$m in immersion, the ghosts in IGRINS will have a peak intensity of 0.2\% of the main peak.  Quantitative lab measurements at 1.523 $\mu$m in immersion were attempted but were not reliable due to nonlinear response at the requisite high dynamic ranges need to measure the low ghost levels.

>>>>

Immersion gratings are diffraction gratings illuminated within a high refractive index optical material, which provides increased spectral resolving power compared to diffraction gratings of comparable size illuminated in air or vacuum.  Scientific demands for high spectral resolving power combined with engineering demands for compact spectrographs make immersion gratings an attractive technology.  This report chronicles the lab performance of CA1a, an immersion grating made of silicon ($n_{Si}\sim3.4$).  CA1a or its spare CA1b will serve as the primary dispersive optical element for the Immersion Grating Infrared Spectrometer, IGRINS\cite{2010SPIE.7735E..54Y}.  We have reported on immersion grating design and fabrication elsewhere\cite{2007ApOpt..46.3400M}.  Wang et al. 2010\cite{2010SPIE.7739E.146W} reported on the science requirements for, fabrication of, and optical testing results of CA1, the parent Si boule puck from which CA1a was cut.  Since 2010 we have cut and polished two optical devices from CA1, and report here on their performance \emph{in immersion}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview} 
Figure \ref{fig:CA1aphoto} shows a photo of the final immersion grating CA1a after cutting, polishing, AR coating, and aluminization.  The trapezoidal side profile is a relic from the shape of the parent substrate and our cutting strategy.  The optically active volume is the prism shown above the dashed line in the photo in Figure \ref{fig:CA1aphoto}.  We left on additional silicon to strengthen the thin end of the prism wedge.  The front entrance face has a multi-layer dielectric anti-reflection (AR) coating, which, based on direct measurements off the CA1a entrance face, has a reflectivity  $<1\%$ across the 1.4$-$2.5 $\mu$m range.  The grating grooves were aluminized with a conformal Al layer.  Cryogenic testing of heritage gratings demonstrated that the conformal layer of Al is robust to typical cryogenic thermal cycling\cite{2007ApOpt..46.3400M}. We have not yet cooled CA1a.

\begin{figure}
  \centering
  \subfloat[CA1a photo]{\label{fig:CA1aphoto}\includegraphics[height=5cm]{chSPIE_2012_CA1/figs/ca1_bartest2}}
	~
%  \subfloat[CA1a drawing]{\label{fig:CA1adraw}\includegraphics[page=1, trim=24cm 15.15cm 2cm 5cm, clip=true, totalheight=0.2\textheight ]{APRA_BOULE_29MM_R3_CA1_X14_2011-03-08}}
   \subfloat[CA1a drawing]{\label{fig:CA1adraw}\includegraphics[height=4cm]{chSPIE_2012_CA1/figs/ca1a_drawing}}
  \caption{Photo and design drawing of the immersion grating CA1a in the lab in August 2011.  The entrance face is on the right, with a light green color in the photo (color available in the digital manuscript), which is due to the AR coating.  The grating surface is on the top with microscopic grating lines perpendicular to the long edge of the grating.  In operation a 25 mm circular beam will be incident on the entrance face and will project into an ellipse on the grating surface as seen in the drawing.  The dispersed light will reemerge from the entrance face.  The units in the drawing are mm.  The parent substrate and grating geometry are pictured in Figures 1, 3, and 4 in Wang et al. 2010\cite{2010SPIE.7739E.146W}.  Those figures reveal how the CA1a trapezoid shape and curved rear edge derive from the parent substrate shape.}
  \label{fig:gram}
\end{figure}

@@

We produce the grating grooves by photolithography and anisotropic chemical wet etching\cite{2007ApOpt..46.3400M,2010SPIE.7739E.146W}.  This process has some special features.  The wet etching process makes acute angle grooves, not 90$^\circ$ grooves, as illustrated in Figure \ref{fig:CA1aSEM}.  The groove apex angle $A=70.5^\circ$ is the intersection of two 111 Si crystal planes.  We anticipated an apex angle widened by 0.8$^\circ$ on both sides, for a net apex angle of about $A=72.1^\circ$.  A finite but small amount of etching accross the 111 crystal planes causes the small 0.8$^\circ$ angular correction\cite[Figure 5]{2007ApOpt..46.3400M}.  The anisotropic correction similarly decreases the blaze angle $\delta$ by $\Delta \delta = 0.8^\circ$.  This effect must be accounted for, first at the time of the initial x-ray orientation and cutting of the parent substrate and second at the time of cutting the immersion prism from the Si parent substrate.  We verified the delivered blaze angle after wet etching but before cutting our immersion grating prism by measuring the relative intensity of eight diffracted orders in reflection in air at the air-Si grating interface.  We made a simple scalar diffraction theory model and compared it to the observed intensity of the eight orders surrounding order 82, the brightest observed order at 632.8 nm in front-surface reflection.  The measurements were performed in the Littrow configuration.  The model predicted the effect of the blaze envelope as a function of incidence angle.  We found $\delta=71.63\pm0.20^\circ$, consistent within the uncertainty with $\delta = R3$, so we cut the front face to R3.  The apex and blaze angles are conspicuous in the SEM cross section (Figure \ref{fig:CA1aSEM}).  Importantly, the groove apex shows a sharp peaked tip with no evidence of a flat bottom, which can occur in incomplete wet etching.  Flat bottoms cause a direct efficiency loss by diffracting light away from the blaze.  In the right panel of Figure \ref{fig:CA1aSEM} the optically active facets are highlighted.  The flat groove tops on the grating surface are artifacts of the groove formation process.  Specifically, nitride coated groove tops serve as anisotropic wet etch dams.  It is clear from the annotated SEM micrograph that the groove tops are shadowed for light incident at or close to the blaze angle.  The groove tops will be shadowed so long as the ratio of the grating top $t$ to pitch $\sigma$ ratio satisfies the condition:
\[ 
\frac{t}{\sigma} < \frac{1}{1+\frac{ \tan (A) }{ \tan (\delta{}) }}, 
 \] 
For our grating, $t/\sigma=0.36<0.49$, so the optically active groove facets fully shadow the groove tops as planned.  The SEM micrographs are not sensitive enough to small ($\sim5$ nm) scale groove position errors, so detailed optical and IR metrology is necessary to evaluate the performance.

%-------------
   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=7cm]{chSPIE_2012_CA1/figs/CA1_SEM_cross3}
   \end{tabular}
   \end{center}
   \caption[CA1a SEM]{ \label{fig:CA1aSEM}  Scanning electron micrograph (SEM) of a $\sim$100 $\mu$m cross section of a scrap portion of the immersion grating CA1.  The left panel is the unaltered SEM.  The right panel is a schematic illustrating the grating specifications and the geometry of incident and diffracted beams (thick black line with arrows).  The beam is incident from the left, and diffracts at the facets at the silicon/aluminum interface.  The incident angle $\alpha$ and diffracted beam $\beta$ are measured from the grating normal (shown in blue).  The blaze angle $\delta$ is set by the orientation of the crystal planes with respect to the grating surface.  This angle was designed to be $\delta=71.56^\circ$, which is the angle whose tangent is 3.  The optically active facets are highlighted as short red vertical lines (\emph{color online}).  The regions of the grating above the dashed line do not see the beam.  In the IGRINS design and in our lab testing there is a small out of plane angle $\gamma$ not shown here.  The apparent hillock artifacts on the grating facets are a result of the cross-section preparation process, the measured\cite{2010SPIE.7739E.146W} surface flatness is 1.7 nm.}
   \end{figure} 
%-------------

\section{Efficiency} 
For optimal performance immersion gratings should be as efficient as possible.  The IGRINS specification for immersion grating efficiency is 65-70\% peak on blaze\cite{2010SPIE.7739E.146W}. We directly measured the AR-coated entrance face reflective loss at $<1\%$ over the measured range $1500-2300$ nm.  From measurements of the microscopic surface roughness\cite{2010SPIE.7739E.146W} we expect scattered light from microscopic surface roughness to be $<0.5\%$.  We directly measured the immersion grating efficiency as a function of wavelength with a custom scanning monochromator setup in our lab, described in the Section \ref{sec:GTA}.  The reference mirror was aluminum on glass, so the absolute grating efficiency is about 3.5\% lower than reported here, assuming aluminum reflectance of 95\% in the near-IR.  Recall that the grating grooves are aluminized, so the reported relative efficiency is a good indicator of how well the bulk of the immersion grating is performing.  The measurement shown in figure \ref{fig:CA1a-efficiency} has 1 nm bandwidth, with 1nm sampling over the range $1500-2300$ nm.  The measured peak on-blaze efficiency is between 70\% and 80\% across all 43 orders, except for order 120 which has a peak efficiency of 68\%.  CA1a was measured with an out of plane angle \cite{schroeder1987}, $\gamma \sim 2.6^\circ$ in immersion.  We only coarsely controlled the incidence angle $\alpha$ in our efficiency measurement, with $\alpha \sim \delta$ to within about 2$^\circ$.  Accordingly, we measured some angularly dependent diffraction loss that one would expect if orders diffracted into the grating sidewalls.  It is best to have $\alpha > \delta$ so that the blaze envelope is centered at $\beta < \delta$.

@@

\section{Refractive index dependence}
The refractive index of silicon is wavelength and temperature dependent, so the blaze pattern in Figure \ref{fig:CA1a-efficiency} will be different at the cryogenic operating temperature of an IR spectrograph.  Precise measurements for crystalline Si are available for the CHARMS group at Goddard\cite{2006SPIE.6273E..77F}.  The right panel of figure \ref{fig:CA1a-diffrac} shows the refractive index as a function of wavelength for 296 K, 273 K, and 77K, using the Sellmeier equation from the Goddard group and assuming vacuum wavelengths.  The index goes from about 3.483 to 3.445 in the wavelength range 1.5 to 2.3 $\mu$m, which is a change of about 1\%.  The index decreases by an average of 0.8\% from room temperature to 77K.  The index intimately controls both the diffraction angle $\beta$ at the Si-Al grating interface via the grating equation, and the refraction angle $\theta$ at the Si-vacuum interface via Snell's law.  For example the wavelength $\lambda=2.290 \;\mu$m at room temperature is diffracted to 78th order near the peak of the blaze.  Reducing the temperature to 77K decreases the index of refraction by 0.8\%. This puts $\lambda= 2.290 \;\mu $m into 77th order, which is at the edge of the blaze.  The grating period $\sigma$ also shrinks by a factor of the coefficient of thermal expansion (CTE) of Si, $\alpha \sim 3\times10^{-6}/^\circ$C.  From room temperature to 77K the fractional shrinkage is about 0.06\%, which is an order of magnitude less than the effect of the index of refraction.  Furthermore, the CTE effect will have no effect at the Si-vacuum interface.

\begin{figure}
\begin{center}
 \begin{tabular}{c}
    \includegraphics[width=1.0\textwidth]{chSPIE_2012_CA1/figs/CA1a_diffrac}
   \end{tabular}
  \end{center}
  \caption[CA1a Diffraction]{\label{fig:CA1a-diffrac} Measured and predicted diffraction angles for CA1a.  The right panel is the index of refraction as a function of wavelength\cite{2006SPIE.6273E..77F} for T = 296, 273, and 77 K.  The left panel is the angular position of diffracted beams as a function of wavelength.  The almost vertical lines are approximately 1 free spectral range of the observed 43 diffraction orders for $1500 < \lambda (\textrm{nm}) < 2300$ in air at T = 296K.  The order numbers for every fifth order, starting at 78th order are marked at the top.  The black diamonds are the observed peaks of the blaze efficiency (cf. figure \ref{fig:CA1a-efficiency}).  The measurements longward and shortward of $\lambda=1870$ nm have slightly different incidence $\alpha$ angles, which jogged the the blaze center positions.  The red $\ast$, green square, and blue $\times$ demarcate the expected positions of beams from scalar optics diffraction and refraction theory assuming a Si refractive index at the temperatures of T=296, 273, and 77 K, respectively.  The model corrects for $\alpha \neq \delta$ measurements for $\lambda < 1870 $ nm, causing a jog in the $\theta(\lambda)$ trend highlighted by the vertical black dashed lines.  The temperature change shifts the position of diffracted beams by an entire order.}
\end{figure}

@@

The major problem with periodic errors is that they cause symmetric ghosts surrounding the main diffraction peak.  The intensity of the ghosts relative to the main peak is related to the periodic error amplitude by\cite{2007ApOpt..46.3400M,james2007,2010SPIE.7739E.146W}:
\begin{eqnarray}
	\frac{I_{\textrm{ghost}}}{I_{\textrm{line}}}= \left \lbrack \frac{2\pi n}{\lambda} \xi \sin{\delta} \right \rbrack ^2
\end{eqnarray}
where $\xi$ is the amplitude of the spacing error.  Figure \ref{fig:PSFzygo} shows a logarithmically scaled PSF from optical interferometry of CA1a in reflection from the aluminized surface in air at 632.8 nm over a 25 mm circular aperture.  The measured intensity of the ghost relative to the main peak is $I_{g}/I_{0}=9\times10^{-4}$.  Optical spectral purity lab measurements at 632.8 nm are higher by 20\%.  Measurements at 543 nm (comparable to 1.87 $\mu$m in immersion), show a level of $I_{g}/I_{0}=1.6\times10^{-3}$, which is 30\% greater than one would expect from scaling interferometrically derived intensity at 632.8 nm.  Extrapolating the interferometrically derived intensity to 1.45 $\mu$m in immersion, the ghosts in IGRINS will have a peak intensity of 0.2\% of the main peak.  Quantitative lab measurements at 1.523 $\mu$m in immersion were attempted but were not reliable due to nonlinear response at the requisite high dynamic ranges need to measure the low ghost levels.
